### 2023-07-27 python_excel_ite.tex
draft ready for detailed final proofreading
fixed missing items in references

Spreadsheet based modeling has transformed the teaching of management science in business schools over the past twenty plus years. The late 1990's saw first editions of game changing textbooks \cite{winstonPracticalManagementScience2018,ragsdaleSpreadsheetModelingDecision2017} focused on the use of spreadsheets in teaching modeling and management science.  A series of conferences focused on teaching management science with spreadsheets started at Dartmouth in 1998 and several presentations from that conference made up the bulk of papers in the first two issues of the INFORMS Transactions on Education (ITE) journal. The next few decades saw numerous textbooks \cite{powellBusinessAnalyticsArt, camm2020business} and teaching papers in journals such as \href{https://pubsonline.informs.org/journal/ited}{ITE}that prominently featured spreadsheet based modeling.

@@

\begin{figure*}[!htbp]
	\centering
	\caption{Notebook cells in edit model}
	\includegraphics[scale=0.5]{images/cells_edit_mode.png}
	\label{fig:cells_edit_mode}
\end{figure*}

\begin{figure*}[!htbp]
	\centering
	\caption{Notebook cells after execution}
	\includegraphics[scale=0.5]{images/cells_after_running.png}
	\label{fig:cells_after_running}
\end{figure*}

@@

There are two overarching learning objectives for this \href{http://www.sba.oakland.edu/faculty/isken/courses/mis6900/mod3a_whatif.html}{first EwP submodule}. Students learn how Python might be used to do something they are quite familiar with doing in a spreadsheet -- model building and sensitivity analysis. At the same time, students encounter, as needed, more advanced Python programming concepts and techniques. In this way, the computational problem to be solved drives the introduction of more advanced Python concepts and techniques instead of such things being presented in a vacuum. I make it a point to show that there are often multiple possible approaches to a computational problem by being willing to abandon one approach and trying another. Emphasis is given to the lessons learned from each path explored. Every notebook is accompanied by screencasts that walk the students through the material and act as a guided tour with challenges to overcome along the way.

@@

Now that we have created some useful modeling functionality, our goal is to make it easier for a modeler to actually use it. Certainly we do not want to rely on copying, pasting and modifying code when building a new model. In the Python world, the natural next step is to deploy our code as a Python \textit{package} \cite{buezenWelcomePythonPackages} that can then be imported like any other Python library.

@@

\section{Software availability}

@@

\section{Classroom experience and the future}

>>>>

Spreadsheet based modeling has transformed the teaching of management science in business schools over the past twenty plus years. The late 1990's saw first editions of game changing textbooks \cite{winstonPracticalManagementScience2018,ragsdaleSpreadsheetModelingDecision2017} focused on the use of spreadsheets in teaching modeling and management science.  A series of conferences focused on teaching management science with spreadsheets started at Dartmouth in 1998 and several presentations from that conference made up the bulk of papers in the first two issues of the INFORMS Transactions on Education (ITE) journal. The next few decades saw numerous textbooks \cite{powellBusinessAnalyticsArt2019, camm2020business} and teaching papers in journals such as \href{https://pubsonline.informs.org/journal/ited}{ITE}that prominently featured spreadsheet based modeling.

@@

\begin{figure*}[!htbp]
	\centering
	\includegraphics[scale=0.5]{images/cells_edit_mode.png}
	\caption{Notebook cells in edit model}
	\label{fig:cells_edit_mode}
\end{figure*}

\begin{figure*}[!htbp]
	\centering
	\includegraphics[scale=0.5]{images/cells_after_running.png}
	\caption{Notebook cells after execution}
	\label{fig:cells_after_running}
\end{figure*}

@@

There are two overarching learning objectives for this \href{http://www.sba.oakland.edu/faculty/isken/courses/mis6900/mod3a_whatif.html}{first EwP submodule}. Students learn how Python might be used to do something they are quite familiar with doing in a spreadsheet -- model building and sensitivity analysis. At the same time, students encounter, as needed, more advanced Python programming concepts and techniques. In this way, the computational problem to be solved drives the introduction of more advanced Python concepts and techniques instead of such things being presented in a vacuum. I make it a point to show that there are often multiple possible approaches to a computational problem by being willing to abandon one approach and trying another. Emphasis is given to the lessons learned from each path explored. Every notebook is accompanied by screencasts that walk the students through the material and act as a guided tour with challenges to overcome along the way. While all of the notebooks are publicly available (see Section \ref{sec:software}), links to an html version of each of the notebooks are provided throughout the document.

@@

Now that we have created some useful modeling functionality, our goal is to make it easier for a modeler to actually use it. Certainly we do not want to rely on copying, pasting and modifying code when building a new model. In the Python world, the natural next step is to deploy our code as a Python \textit{package} \cite{buezenWelcomePythonPackages2022} that can then be imported like any other Python library.

@@

\section{Software availability}
\label{sec:software}

@@

\section{Classroom experience and the future}
\label{sec:classroom}
